\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-04-30 trunk/arch.tex
updates

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash
\kcomment{(\ie as it works to complete a goal)}if
the internal state of the plan gets out of synch with the actual state
of the world. As a result the planning problem managed {\em in situ}
has traditionally remained fairly detached from low-level
control. Most adaptations at the lower-level reactive layers in
contrast are managed by specialized components (for example
\texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner. The \rx architecture contributes to agent
architectures over and beyond \texttt{IDEA} in the following
\kcomment{significant} ways:

>>>>

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash
\footnote{\kcomment{In such an event as the planner works towards goal
    satisfaction, the initial conditions leading to achieve that goal
    are no longer valid. The planner then tries to achieve a different
    goal which too has to be discarded similarly. And so on.}}  if the
internal state of the plan gets out of synch with the actual state of
the world.

\kcomment{A important consequence of this has been that} the planning
problem managed {\em in situ} has traditionally remained fairly
detached from low-level control. Most adaptations at the lower-level
reactive layers in contrast are managed by specialized components (for
example \texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner. The \rx architecture contributes to agent
architectures over and beyond \texttt{IDEA} in the following
\kcomment{significant} ways:
